---
title: "Shiny app for plotting distributions of proportions defined by normal distributions on the logit scale"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package installation and update

The easiest way to install the `logitnormdistapp` package is from Github. This requires installing the `devtool` package first.

```{r, eval = FALSE, message=FALSE}
install.packages("devtools")
```

Then load the `devtool` package:

```{r, eval = FALSE}
library(devtools)
```

In order to install (or update) the `logitnormdistapp` package, run the following line:

```{r, eval = FALSE}
install_github("AurMad/logitnormdistapp")
```

## The `shiny_logitnorm()` function

The package contains a single function called `shiny_logitnorm()`. This function launches a shiny app. The user can specify either the mean and standard deviations of a normal distributions on the logit scale using sliding bars. The corresponding distribution of proportions will be plotted and the corresponding mean and sigma parameters will be displayed. The user can also enter the mean and sigma parameters which will lead to the corresponding distribution being displayed.

```{r, eval = FALSE}
library(logitnormdistapp)

shiny_logitnorm()
```
